DNNNNR0: How to Avoid OOTA Without Really Trying

### 2025-03-07 paper/ootavacuous.tex
ootashort: Convert from ASPLOS to C++ working paper
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\begin{document}
\title{How to Avoid OOTA Without Really Trying}

@@

\author{
Alan Stern (stern@rowland.harvard.edu) \and
Paul E.~McKenney (paulmck@kernel.org) \and
Michael Wong (fraggamuffin@gmail.com)
}

@@

	It follows that enforcing OOTA avoidance requires no special
	action from implementations and no changes to user code or
	to the standard.
\end{abstract}
\maketitle{}

@@

Therefore, this paper's contribution is to show how these
constraints prevent real-world C++ implementations doing per-thread
analysis from exhibiting OOTA behavior, and not with minimal
cost~\cite{PiezhaoOu2018OOTApapl}, but rather with no cost at all.
\emph{@@@ Are these the right qualifiers?}

@@

>>>>

\begin{document}
\title{DNNNNR0: How to Avoid OOTA Without Really Trying}

@@

\author{
Alan Stern \and
Paul E.~McKenney \and
Michael Wong \and
Maged Michael
}

@@

	It follows that enforcing OOTA avoidance requires no special
	action from implementations and no changes to user code or
	to the standard.

	Audience: SG1.
\end{abstract}
\maketitle{}

@@

Therefore, this paper's contribution is to show how these
constraints prevent real-world C++ implementations doing per-thread
analysis from exhibiting OOTA behavior, and not with minimal
cost~\cite{PiezhaoOu2018OOTApapl}, but rather with no cost at
all~\cite{PaulEMcKenney2023P3046R2/OOTAwithoutTrying}.
\emph{@@@ Are these the right qualifiers?}

@@

\section*{History}

This paper is a condensation of P3064R2 ("How to Avoid OOTA Without
Really Trying")~\cite{PaulEMcKenney2023P3046R2/OOTAwithoutTrying}.
It also adds citations and clarifications.
